Research paper

### 2013-01-07 Research paper.tex
RP: Fowlt corrections

\begin{itemize}
\item \emph{The direct approach} does very little source language analysis, and could thus be viewed as the automated version of looking up every word in the source language in a dictionary and replacing it with the corresponding word in the target language. This often does not yield very good results: if I for example would have translated this paper from my mother tongue Dutch to English word for word, 'would we now not real a good result have'. It should be noted, however, that the direct approach mostly is more complicated than this; for example, in some cases morphological analysis is needed before it can be looked up in a dictionary, and more morphological analysis is needed for the translation word to fit in the sentence. Word reordering rules can also be included.
\item \emph{The syntactic approach} tries to discover the syntactic structure of the source sentence before it starts translating, using a parser. This structure is then translated to the target language, and filled with translated words.
\item \emph{The semantic approach} goes even one step further and also tries to grasp the meaning of a sentence, roughly. A sentence like \emph{Mummy kisses daddy} for example entails that mummy is the agent, and daddy the patient of the sentence. After having identified these semantic roles, the algorithm would then look how this meaning is expressed in the target language, find the approriate syntactic structure for that, and fill it with the translated words.
\item \emph{The interlingua approach}. All of the approaches so far have in common that they require a separate rule set for each language pair; no or very few rules included for translations from English to German can also be used for translations from English to French. This means that for every time a new language is added to the system, the amount of rules that have to be added grows exponentially. The Interlingua approach is an attempt to solve this problem, by pairing up every language with a formal representation of meaning, the Interlingua. This means a translation from English to German would entail a translation from English to the Interlingua (using the ruleset English $\rightarrow$ Interlingua) and then a translation from the Interlingua to German (using the ruleset Interlingua $\rightarrow$ German). When translating from English to French, the same two steps would be taken, and the same ruleset English $\rightarrow$ Interlingua can be used.
\end{itemize}

@@

\begin{itemize}
\item Optimization of how the various the n-grams and skipgrams are saved in memory. By reserving the labels that do not take a lot of memory for the most frequent grams, a lot of memory can be saved.
\item For trigrams and larger n-grams, taking into account the frequencies of the parts. If these parts do not exist or are very infrequent, there is no use in looking for the whole - if even the parts do not exist, the whole will not exist for sure and doesnt need to be investigated any further.
\end{itemize}

>>>>

\begin{itemize}
\item \emph{The direct approach} does very little source language analysis, and could thus be viewed as the automated version of looking up every word in the source language in a dictionary and replacing it with the corresponding word in the target language. This often does not yield very good results: if I for example would have translated this paper from my mother tongue Dutch to English word for word, 'would we now not real a good result have'. It should be noted, however, that the direct approach mostly is more complicated than this; for example, in some cases morphological analysis is needed before it can be looked up in a dictionary, and more morphological analysis is needed for the translation word to fit in the sentence. Word reordering rules can also be included.
\item \emph{The syntactic approach} tries to discover the syntactic structure of the source sentence before it starts translating, using a parser. This structure is then translated to the target language, and filled with translated words.
\item \emph{The semantic approach} goes even one step further and also tries to grasp the meaning of a sentence, roughly. A sentence like \emph{Mummy kisses daddy} for example entails that mummy is the agent, and daddy the patient of the sentence. After having identified these semantic roles, the algorithm would then look how this meaning is expressed in the target language, find the appropriate syntactic structure for that, and fill it with the translated words.
\item \emph{The interlingua approach}. All of the approaches so far have in common that they require a separate rule set for each language pair; no or very few rules included for translations from English to German can also be used for translations from English to French. This means that for every time a new language is added to the system, the amount of rules that have to be added grows exponentially. The Interlingua approach is an attempt to solve this problem, by pairing up every language with a formal representation of meaning, the Interlingua. This means a translation from English to German would entail a translation from English to the Interlingua (using the ruleset English $\rightarrow$ Interlingua) and then a translation from the Interlingua to German (using the ruleset Interlingua $\rightarrow$ German). When translating from English to French, the same two steps would be taken, and the same ruleset English $\rightarrow$ Interlingua can be used.
\end{itemize}

@@

\begin{itemize}
\item Optimization of how the various the n-grams and skipgrams are saved in memory. By reserving the labels that do not take a lot of memory for the most frequent grams, a lot of memory can be saved.
\item For trigrams and larger n-grams, taking into account the frequencies of the parts. If these parts do not exist or are very infrequent, there is no use in looking for the whole - if even the parts do not exist, the whole will not exist for sure and does not need to be investigated any further.
\end{itemize}
